### 2015-09-03 Projects/DelCo_2012/Report/DelCo_2012.tex
update delco 2012 writeup

After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that the majority of the

@@

>>>>

After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream positioned {\bf here} the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (cf. Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}). Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distrubtion of water is far more dispered around the gas cooling room. The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.

@@

\chapter{Spray Denisty Figures}
\label{app:spray_density}
